Homework 8

### 2019-11-05 hw8/MSimonsHW8.tex
hw8 problem 1b
hw8 problem 1c

\item TODO
\item TODO

>>>>

\item Consider $\mathbb{Z}/2\mathbb{Z}$.  If $f(x) = x^3 + 2x^2 - x + 1$, then
$\overline{f}(x) = x^3 - x + 1$.  We know that $\overline{f}(x)$ is
irreducible in $\mathbb{Z}/2\mathbb{Z}$ because
$\overline{f}(0) = \overline{f}(1) = 1$.  Since $\overline{f}(x)$ is
irreducible in $\mathbb{Z}/2\mathbb{Z}$, $f(x)$ is irreducible in $\mathbb{Q}$,
which means that $\mathbb{Q}[x]/(x^3 + 2x^2 - x + 1)$ is a field.

\item Only first-degree and second-degree polynomials can be irreducible in
$\mathbb{R}[x]$.  Since $(x^5 + 42x^4 + \pi x^3 -1729x^2 + ln(2)x - 2019)$
is a fifth-degree polynomial, it is reducible in $\mathbb{R}[x]$.  Therefore
$\mathbb{R}[x]/(x^5 + 42x^4 + \pi x^3 -1729x^2 + ln(2)x - 2019)$ is NOT
a field.
